---
title: "dev_history.Rmd for working package"
author: "Cervan Girard"
date: "06/10/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
library(ps)
library(dplyr)
library(stringr)
```

<!--
# Description of your package

This will fill the description of your package.
--> 

```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "R session tracking tool for RSworkbench",
    Description = "Tracking sessions around users to know what's going on.",
    `Authors@R` = c(
      person("Cervan", "Girard", email = "cervan@thinkr.fr", role = c("aut", "cre"), comment = c(ORCID = "0000-0002-4816-4624")),
      person(given = "ThinkR", role = "cph")
    )
  ),
  overwrite = TRUE
)
# Define License with use_*_license()
usethis::use_mit_license("Cervan Girard")
```

# Read data

<!-- Store your dataset in a directory named "inst/" at the root of your project -->
<!-- Use it for your tests in this Rmd thanks to `load_all()` to make it available
and `system.file()` to read it in your examples 
-->

```{r development-2}
# Run all in the console directly
# Create "inst/" directory
dir.create(here::here("inst"))
# Example dataset
# file.copy(system.file("nyc_squirrels_sample.csv", package = "fusen"), here::here("inst"))
# Make your dataset file available to the current Rmd
pkgload::load_all(path = here::here(), export_all = FALSE)
# You will be able to read your example data file in each of your function examples and tests as follows
# datafile <- system.file("nyc_squirrels_sample.csv", package = "beaware")
# nyc_squirrels <- read.csv(datafile)
```


# Récupérer les informations pour monitorer


```{r development}
ok <- ps() %>% 
  filter(stringr::str_detect(name , "^rsession$"))

### il manque le pourcentage CPU et MEM

test <- system("ps -C rsession -o 'pid,%cpu,%mem'", intern = TRUE) %>% 
  str_replace_all("\\s+", " ") %>%
  str_trim() %>% 
  str_split(" ") 


ok_bis <- map_df(test[-1], ~ set_names(.x, tolower(test[[1]])) ) %>% 
  mutate_at(c("pid", "%mem", "%cpu"), as.numeric)


mem_cpu <- left_join(ok, ok_bis, by = "pid") 

## Avoir la version de R
  
map_df(ok$pid, function(x){
  cmd <- paste0("cat /proc/",x,"/environ")
  r_version <- system(cmd, intern = TRUE) %>% 
    str_extract(".+/R/(.+\\d.\\d.\\d|\\d.\\d.\\d)") %>% 
    str_extract("\\d.\\d.\\d")
  data.frame("pid" = x, r_version = r_version)
}) %>% 
  right_join(x = mem_cpu, by = "pid")

```



```{r function}
#' Get processes rsession
#'
#'
#' @return
#' data frame of process rsession
#' @export
#'
#' @importFrom ps ps
#' @importFrom dplyr filter
#' @importFrom stringr str_detect
#' @examples
get_process_rsession <- function() {
  ps() %>% 
    filter(str_detect(name , "^rsession$"))
}
```

```{r examples}
get_process_rsession()
```

```{r tests}
test_that("Test get_process_info", {
  process <- get_process_rsession()
  expect_is(process, "data.frame")
  expect_true(all(c("pid", "username") %in% names(process)))
})
```

# Get cpu and mem info

```{r function-2}
#' Get cpu and mem info
#'
#'
#' @return
#' data frame of process rsession
#' @export
#'
#' @importFrom attempt attempt
#' @importFrom dplyr mutate_at
#' @importFrom purrr map_df set_names
#' @importFrom stringr str_replace_all str_trim str_split
#' @examples
get_mem_cpu <- function(){
  process <-  attempt(
    system("ps -C rsession -o 'pid,%cpu,%mem'", intern = TRUE), 
    msg = "Cannot run ps command in terminal, please chek your rights"
  )
  
  result_process <- process %>% 
    str_replace_all("\\s+", " ") %>%
    str_trim() %>% 
    str_split(" ") 
  
  
  map_df(
    result_process[-1],
    ~ set_names(.x, tolower(result_process[[1]]))
  ) %>% 
    mutate_at(c("pid", "%mem", "%cpu"), as.numeric)
}
```

```{r examples-2}
get_mem_cpu()
```


```{r tests-2}
test_that("Test get cpu mem info", {
  process <- get_mem_cpu()
  expect_is(process, "data.frame")
  expect_true(all(c("pid", "%cpu", "%mem") %in% names(process)))
})
```


# Get r info

```{r function-3}
#' Get r version for rsession
#'
#' @param pids vector of pids of rsessions
#'  
#' @return
#' data frame of process rsession
#' @export
#'
#' @importFrom attempt attempt
#' @importFrom stringr str_extract
#' @importFrom purrr map_df
#'
#' @examples
get_r_version <- function(pids){
  
  map_df(pids, function(x){
    
    cmd <- paste0("cat /proc/",x,"/environ")
    
    r_version <- attempt(system(cmd, intern = TRUE), msg = "Cannot run cat of /proc/pid, please check your rights") %>% 
      str_extract(".+/R/(.+\\d.\\d.\\d|\\d.\\d.\\d)") %>% 
      str_extract("\\d.\\d.\\d")
    data.frame("pid" = x, r_version = r_version)
  }) 
}
```

```{r examples-3}
pids <- get_process_rsession()
get_r_version(pids$pid)
```


```{r tests-3}
test_that("Test get r version of rsession", {
  pids <- get_process_rsession()
  
  process <- get_r_version(pids$pid)
  expect_is(process, "data.frame")
  expect_true(all(c("pid", "r_version") %in% names(process)))
})
```

# Get all info

```{r function-4}
#' Get all info about meme and cpu rsession
#'
#' @return data.frame
#' @export
#'
#' @importFrom dplyr left_join
#'
#' @examples
get_all_info <- function(){
  r_process <- get_process_rsession()
  r_version <- get_r_version(r_process$pid)
  cpu_mem <-  get_mem_cpu()
  
  r_process %>% 
    left_join(r_version, by = "pid") %>% 
    left_join(cpu_mem, by = "pid")
}
```

```{r examples-4}
get_all_info()
```

```{r tests-4}
test_that("my_function works properly", {
  process <- get_all_info()
  expect_is(process, "data.frame")
  expect_true(all(c("pid", "r_version", "%cpu", "%mem", "username") %in% names(process)))
})
```

If take too much time
```{r}
microbenchmark::microbenchmark(get_all_info())
```


# There can be development actions

These will be included in the `dev_history.R` file of your package, but won't be direct part of it.

```{r development-1, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(rmd = "dev/dev_history.Rmd")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
